CTL mapping - The added value from segregating correlation

### 2012-01-30 inst/methodPaper/document.tex
Updates to the text

\emph{ {\bf Materials}}
  Metabolite data from an \emph{A. Thaliana} Landsberg erecta (Ler) and Cape Verde Islands (Cvi) 
  dataset from R/qtl, 24 characterized metabolites which are the products of chain elongation. 
  There are 162 recombinant inbred lines genotyped at 117 markers on 5 chromosomes. Additional 
  details about the experimental settings are available in the original paper \cite{Keurentjes:2006,AlonsoBlanco:1998}
\vspace{-0.6cm}
\section{Results}
  CTL mapping was performed and a per trait CTL thresholds of $P < 0.001$ was 
  determined by using 15,000 permutations.
  Information obtained by CTL mapping is shown in the trait to trait interaction matrix (Fig. \ref{subfigb}).
  The CTL profiles were combined with QTL information, leading to the following observations \ref{subfiga}:\\
  1) Additional CTL found, where no QTL was present (Fig \ref{subfiga} - Peak 1). Loss of variation in the genes 
  underneath the CTL are not causing variation differences in the observed trait, CTL is able to 
  detect the differences in correlation.\\
  2) CTL co-localized with QTL, in this situation CTL gives a detailed view of which traits 
  are contributing variation to the observed QTL  (Fig \ref{subfiga} - Peak 3).\\
  3) QTL with no CTL  (Fig \ref{subfiga} - Peak 2), we interpret this as the source of the variation. Analysis in this way of 
  all 24 Single trait CTL profiles combined with their QTL profiles allows us to reconstruct the 
  source of natural variation and follow it down the network.

\emph{ {\bf Network reconstruction}}
  Using the previously decribed method to draw the arrows between traits, we reconstruct the interaction 
  network amongst the 24 metabolities in Arabidopsis (Fig. \ref{subfigc}). We observe that our network is 
  composed of 2 parts which seem connected only by a just significant CTL from X3.Benzoyloxypropyl to 
  Quercetin.deoxyhexosyl.dihexoside.

>>>>

\emph{ {\bf Materials}}
  Metabolite data from an \emph{A. Thaliana} Landsberg erecta (Ler) and Cape Verde Islands (Cvi) 
  dataset from R/qtl, 24 characterized metabolites which are the products of chain elongation. 
  There are 162 recombinant inbred lines genotyped at 117 markers on 5 chromosomes. Additional 
  details about the experimental settings are available in the original paper \cite{Keurentjes:2006,AlonsoBlanco:1998}
\vspace{-0.6cm}
\section{Results}
  CTL mapping was performed and a per trait CTL thresholds of $P < 0.001$ was 
  determined by using 15,000 permutations.
  When combining CTL and QTL information, we observe:\\
  1) Additional CTL found, where no QTL was present (Fig \ref{subfiga} - Peak 1). Loss of variation in the genes 
  underneath the CTL are not causing variation differences in the observed trait, CTL is able to 
  detect the differences in correlation.\\
  2) CTL co-localized with QTL, in this situation CTL gives a detailed view of which traits 
  are contributing variation to the observed QTL  (Fig \ref{subfiga} - Peak 3).\\
  3) QTL with no CTL  (Fig \ref{subfiga} - Peak 2), we interpret this as the source of the variation. Analysis in this way of 
  all 24 Single trait CTL profiles combined with their QTL profiles allows us to reconstruct the 
  source of natural variation and follow it down the network.

  Information obtained by CTL mapping is shown in the trait to trait interaction matrix (Fig. \ref{subfigb}).

\emph{ {\bf Network reconstruction}}
  Using the information from CTL and QTL we are able to draw arrows between traits, reconstruct the interaction 
  network amongst the 24 metabolities in Arabidopsis (Fig. \ref{subfigc}). We observe that our network is 
  composed of 2 parts which seem connected only by a just significant CTL from X3.Benzoyloxypropyl to 
  Quercetin.deoxyhexosyl.dihexoside.
